---
title: "Trending_Videos_On_Youtube"
author: "Bill_Wu"
date: "03/10/2022"
output: pdf_document
---


```{r warning = FALSE, message = FALSE}

library(tidyverse)
library(ggplot2)
library(utils)
```



```{r warning = FALSE, message = FALSE}

youtube_data <- read_csv("data/Trending_videos_on_youtube_dataset.csv")

```


```{r ewarning = FALSE, message = FALSE}

top10video <- youtube_data %>% 
  arrange(desc(viewCount)) %>%
  head(10)

ggplot(data = top10video, aes(x = reorder(videoTitle, viewCount), y = viewCount)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  ggtitle("Top 10 Most Viewed Videos") +
  ylab("Views") +
  xlab("Video Title") + 
  
  # changing all labels font 
  #theme(text = element_text(size = 8)) +
  
  theme(axis.text = element_text(size = 4))

```

```{r warning = FALSE, message = FALSE}

youtube_data1 <- group_by(youtube_data, channelTitle)

top10channel <- summarise(youtube_data1, TotalViews = sum(viewCount)) %>%
    arrange(desc(TotalViews)) %>%
    head(10)

ggplot(data = top10channel, aes(x = reorder(channelTitle, TotalViews), y = TotalViews)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  ggtitle("Top 10 Most Viewed Channel") +
  ylab("Views") +
  xlab("Channel")


```


```{r warning = FALSE, message = FALSE}


top10likechannel <- summarise(youtube_data1, TotalLike = sum(likeCount)) %>%
    arrange(desc(TotalLike)) %>%
    head(10)

ggplot(data = top10likechannel, aes(x = reorder(channelTitle, TotalLike), y = TotalLike)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  ggtitle("Top 10 Most Liked Channel") +
  ylab("Likes") +
  xlab("Channel")


```


```{r warning = FALSE, message = FALSE}


top10commentchannel <- summarise(youtube_data1, TotalComment = sum(commentCount)) %>%
    arrange(desc(TotalComment)) %>%
    head(10)

ggplot(data = top10commentchannel, aes(x = reorder(channelTitle, TotalComment), y = TotalComment)) +
  geom_bar(stat = "identity", fill = "blue") +
  coord_flip() +
  ggtitle("Top 10 Most Comment Channel") +
  ylab("Comments") +
  xlab("Channel")


```


PsychedSubstance has the most views, likes and most viewd video in their channel. However, Black Pigeon Speaks seems to have a higher number in comments compared to the channel PsychedSubstance. We think the reason could be the difference in their channel category where Black Pigeon Speaks is a news&politics channel whereas PsychedSubstance is a Science&technology/entertainment channel.



```{r warning = FALSE, message = FALSE}


youtube_Category <- youtube_data %>% count(videoCategoryLabel)


ggplot(youtube_Category, aes(x="", y=n, fill=videoCategoryLabel))+
  geom_bar(stat="identity", width = 1, color="white")+
  coord_polar("y", start = 0) +
  theme_void()

```



